Lens Modeling in \sw

### 2014-06-27 text/partC.tex
typo fixes

The presentation of the arrival-time surface in \S\secref{Fermat}
and \secref{arriv} omitted some details for the sake of a more
intuitive explanation.  Specifically, the geometric time delay $t_{\rm
geom}$ and the convergence $\kappa$ were left as proportionalities
(equations
\ref{eq:tgeom} and \ref{eq:kappa}), and the gravitational time delay
$t_{\rm grav}$ was given in an implicit form (equation
\ref{eq:tgrav}).  We now fill in the details.

>>>>

The presentation of the arrival-time surface in
Sections~\ref{sec:Fermat} and \ref{sec:arriv} omitted some details for
the sake of a more intuitive explanation.  Specifically, the geometric
time delay $t_{\rm geom}$ and the convergence $\kappa$ were left as
proportionalities (equations
\ref{eq:tgeom} and \ref{eq:kappa}), and the gravitational time delay
$t_{\rm grav}$ was given in an implicit form (equation
\ref{eq:tgrav}).  We now fill in the details.
